---
title: "STAT 218 Lab Assignment 1"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
format: pdf
execute:
  echo: true
---


## Lab Assignment 1

In this assignment, we will work with the data available in the package of `palmerpenguins`. Let's install and use that package. And let's load our data into R by using `data()` function.

Run the code chunk below. **DO NOT FORGET TO RENDER YOUR QUARTO DOCUMENT TO PDF!**

```{r}
#| include: false
install.packages("palmerpenguins" , repos = "http://cran.us.r-project.org")
library(palmerpenguins)
data("penguins") 
```

**NOTE:** Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.

**Question 0: Please add a code chunk below and add necessary `install.packages()` and `library()` functions (look at the Slide 9). If you skip this part, your functions will not work.**

Add your code chunk here.

**Question 1: Please use `glimpse()`function and write 2-3 sentences to explain what you see.**


```{r}

# Put your R Code Chunk here. 

```


Type your answer (2-3 sentences) here.


**Question 2: How many variables and cases do this dataset have?**

```{r}

# Put your R Code Chunk here. 

```


Type your answer here.


**Question 3: What types of variables are there in this data set? Identify each variable below (categorical, categorical - binary, quantitative)**

**species:**

**island:**

**bill_length_mm:**

**bill_depth_mm:**

**body_mass_g:**

**flipper_length_mm:**

**sex:**

**year:**


**Question 4: Calculate the mean and median values for `bill_length_mm`.**  
*(Hint: You will see `NA` values when you run the function because of missing data. Use the Console Pane by typing `?mean` to find which argument is helpful for removing NAs.)*


```{r}

# Put your R Code Chunk here. 

```

**Question 5: Please create a bar chart by using `ggplot()` function for the variable `species`.**

```{r}

# Put your R Code Chunk here.

```
